An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 VLDB2026/main.tex
change multi modal
Update main.tex

	In contrast, algorithms with low sensitivity to attribute distribution incorporate smarter indexing designs or adaptive query strategies to mitigate these challenges. Milvus, for example, leverages a built-in query optimizer that dynamically determines whether to filter by attributes or search vectors first, based on the selectivity of the query, thus ensuring more robust performance. Other approaches enhance robustness by separating attribute and vector indexing into distinct stages: UNG uses a logical graph to navigate attribute relationships, while CAPS employs an attribute frequency tree to adapt to power-law patterns. For ACORN--\(\gamma\), during index construction, attributes are primarily used for pruning in the lowest-layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected. Consequently, changes in attribute distribution have minimal impact on overall performance.}}

@@

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
		\caption{Multi-Modal}
		\label{fig:attribute-multimodal} 
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
		\caption{Cross-Platform}
		\label{fig:attribute-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
		\caption{Big Dataset}
		\label{fig:attribute big dataset}
	\end{minipage}
\end{figure*}

@@

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
		\caption{Multi-Modal}
		\label{fig:range-multimodal} 
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
		\caption{Cross-Platform}
		\label{fig:range-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
		\caption{Big Dataset}
		\label{fig: range big dataset}
	\end{minipage}
\end{figure*}

>>>>

	In contrast, algorithms with low sensitivity to attribute distribution incorporate smarter indexing designs or adaptive query strategies to mitigate these challenges. Milvus, for example, leverages a built-in query optimizer that dynamically determines whether to filter by attributes or search vectors first, based on the selectivity of the query, thus ensuring more robust performance. Other approaches enhance robustness by separating attribute and vector indexing into distinct stages: UNG uses a logical graph to navigate attribute relationships, while CAPS employs an attribute frequency tree to adapt to power-law patterns. In ACORN--\(\gamma\), during index construction, attributes are primarily used for pruning in the lowest-layer graph, while the upper-layer hierarchical navigation graphs remain largely unaffected. Consequently, changes in attribute distribution have minimal impact on overall performance.}}

@@

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
		\caption{Multi-Modal Datasets}
		\label{fig:attribute-multimodal} 
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
		\caption{Different Platforms}
		\label{fig:attribute-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
		\caption{Large-Scale Dataset}
		\label{fig:attribute big dataset}
	\end{minipage}
\end{figure*}

@@

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
		\caption{Multi-Modal Datasets}
		\label{fig:range-multimodal} 
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
		\caption{Different Platforms}
		\label{fig:range-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
		\caption{Large-Scale Dataset}
		\label{fig: range big dataset}
	\end{minipage}
\end{figure*}
